Shapes analysis for time series.

### 2024-10-14 NEURIPS24/neurips_2024_to_submit.tex
update

% ready for submission
\usepackage{neurips_2024}

@@

\author{%
  David S.~Hippocampus\thanks{Use footnote for providing further information
    about author (webpage, alternative address)---\emph{not} for acknowledging
    funding agencies.} \\
  Department of Computer Science\\
  Cranberry-Lemon University\\
  Pittsburgh, PA 15213 \\
  \texttt{hippo@cs.cranberry-lemon.edu} \\
  % examples of more authors
  % \And
  % Coauthor \\
  % Affiliation \\
  % Address \\
  % \texttt{email} \\
  % \AND
  % Coauthor \\
  % Affiliation \\
  % Address \\
  % \texttt{email} \\
  % \And
  % Coauthor \\
  % Affiliation \\
  % Address \\
  % \texttt{email} \\
  % \And
  % Coauthor \\
  % Affiliation \\
  % Address \\
  % \texttt{email} \\
}
\input{header.tex}
\input{def.tex}
\newcommand\sam[1]{\textcolor{blue}{#1}}
\newcommand\thi[1]{\textcolor{orange}{#1}}
\begin{document}

\maketitle
%In this paper, we propose an unsupervised representation method (TS-LDDMM) to analyze inter-individual variability of time series dataset.
    %Inspired by the shape analysis literature, we extend Large Deformation Diffeomorphic Metric Mapping (LDDMM) to time series, considering the temporal evolution as their distinctive feature.  
    % Given a dataset of $N$ individual's time series $(s^j)_{j\in[N]}$,
    %  we learn a time series of reference $\mathbf{s}_0$ encoding the common part of the individuals as well as diffeomorphisms $(\phi^j)_{j\in[N]}$ encoding the specificities of each individual:
    %  $s^j$ is seen as the transformation of $\mathbf{s}_0$ by $\phi_j$.
    %  Then, the parameters $(\alpha_j)_{j\in[N]}$ encoding the diffeomorphisms $(\phi^j)_{j\in[N]}$ are used as the features representation related to each time series $s^j$.
    %At the crossroads between URL for time series and shape analysis. %the algorithm extends the Large Deformation Diffeomorphic Metric Mapping (LDDMM) to the case of time series. This extension is a nontrivial application of the LDDMM framework since it involves applying deformations to the graph of time series, which have more structure than curves due to the inclusion of the temporal dimension.

@@

\input{paper.tex}

@@

\begin{ack}
Use unnumbered first level headings for the acknowledgments. All acknowledgments
go at the end of the paper before the list of references. Moreover, you are required to declare
funding (financial activities supporting the submitted work) and competing interests (related financial activities outside the submitted work).
More information about this disclosure can be found at: \url{https://neurips.cc/Conferences/2024/PaperInformation/FundingDisclosure}.

>>>>

% ready for submission
\usepackage[final]{neurips_2024}

@@

\author{%
  Thibaut Germain \thanks{Corresponding author. Contact at \texttt{thibaut.germain@ens-paris-saclay.fr}} \\
  Centre Borelli, ENS Paris-Saclay\\
  4 av. des sciences, 91190 \\
  %\texttt{thibaut.germain@ens-paris-saclay.fr} \\
  % examples of more authors
  \And
  Samuel Gruffaz \\
  Centre Borelli, ENS Paris-Saclay\\
  4 av. des sciences, 91190 \\
  % Address \\
  %\texttt{samuel.gruffaz@ens-paris-saclay.fr} \\
  \AND
  Charles Truong \\
  Centre Borelli, ENS Paris-Saclay\\
  4 av. des sciences, 91190 \\
  %\texttt{charles.truong@ens-paris-saclay.fr} \\
  \And
  Laurent Oudre \\
  Centre Borelli, ENS Paris-Saclay\\
  4 av. des sciences, 91190 \\
  \And
  Alain Durmus \\
  CMAP, CNRS, Ecole polytechnique\\
  Institut Polytechnique de Paris\\
  91120 Palaiseau, France \\
}
\input{header.tex}
\input{def.tex}
\newcommand\sam[1]{\textcolor{blue}{#1}}
\newcommand\thi[1]{\textcolor{orange}{#1}}
\begin{document}

\maketitle
%In this paper we propose an unsupervised representation method (TS-LDDMM) to analyze inter-individual variability of time series dataset.
    %Inspired by the shape analysis literature, we extend Large Deformation Diffeomorphic Metric Mapping (LDDMM) to time series, considering the temporal evolution as their distinctive feature.  
    % Given a dataset of $N$ individual's time series $(s^j)_{j\in[N]}$,
    %  we learn a time series of reference $\mathbf{s}_0$ encoding the common part of the individuals as well as diffeomorphisms $(\phi^j)_{j\in[N]}$ encoding the specificities of each individual:
    %  $s^j$ is seen as the transformation of $\mathbf{s}_0$ by $\phi_j$.
    %  Then, the parameters $(\alpha_j)_{j\in[N]}$ encoding the diffeomorphisms $(\phi^j)_{j\in[N]}$ are used as the features representation related to each time series $s^j$.
    %At the crossroads between URL for time series and shape analysis. %the algorithm extends the Large Deformation Diffeomorphic Metric Mapping (LDDMM) to the case of time series. This extension is a nontrivial application of the LDDMM framework since it involves applying deformations to the graph of time series, which have more structure than curves due to the inclusion of the temporal dimension.

@@

\input{paper.tex}
\begin{ack}
  Use unnumbered first level headings for the acknowledgments. All acknowledgments
  go at the end of the paper before the list of references. Moreover, you are required to declare
  funding (financial activities supporting the submitted work) and competing interests (related financial activities outside the submitted work).
  More information about this disclosure can be found at: \url{https://neurips.cc/Conferences/2024/PaperInformation/FundingDisclosure}.

@@

\newpage
